
	\documentclass{res}
	\usepackage{fancyhdr}
	\usepackage{fontspec}
	\usepackage{multicol}
	\usepackage{setspace}
	\usepackage[hidelinks]{hyperref}
	\usepackage{enumitem}
	\setlength{\textwidth}{6.5in}
	
	\newcommand{\HRule}{\rule{\linewidth}{0.25pt}}
	\newsectionwidth{0.0in}
	\sectionskip=0.15in

	
	
	\begin{document}
	\renewcommand{\headrulewidth}{0.0pt}
	
	% Center the name over the entire width of resume:
	\moveleft.5\hoffset\centerline{\large L\small {AKSHMAN} \large A\small {NUMOLU} }
	\moveleft.5\hoffset\centerline{\url{ https://lakshmananumolu.com }}
	\moveleft.5\hoffset\centerline{ \href{mailto:anumolu@uwalumni.com}{anumolu@uwalumni.com} }
	
	\begin{resume}
	
	
	% Summary
	\section{\sc \large A\small {BOUT} \large M\small {E} } \smallskip
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt} \vskip -0.15in
	Hi this is about me
	
	
	
	
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% Publications %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\sc \large P\small {UBLICATIONS} } \smallskip
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt} \vskip -0.05in
    \begin{itemize}[leftmargin=0pt]
    \setlength{\itemsep}{2pt} \smallskip
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Publication 0 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] **Lakshman Anumolu**, Mario F. Trujillo. Gradient augmented level set method for phase change simulations. {\it Journal of Computational Physics}, 353:377-406, 2018.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Publication 1 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] Mario F. Trujillo, **Lakshman Anumolu**, Douglas Ryddner. {\it Direct Numerical Simulations For Two-Phase Flows With Phase Change}, volume 3 of {\it Encyclopedia of Two-Phase Heat Transfer and Flow}. World Scientific, 2018.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Publication 2 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] Mario F. Trujillo, **Lakshman Anumolu**, Douglas Ryddner. The distortion of the level set gradient under advection. {\it Journal of Computational Physics}, 334:81-101, 2017.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Publication 3 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] Steven R. Lewis, **Lakshman Anumolu**, Mario F. Trujillo. Numerical Simulation of Droplet Train and Free Surface Jet Impingement. {\it International Journal of Heat and Fluid Flow}, 44:610-623, 2013.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Publication 4 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] **Lakshman Anumolu**, Mario F. Trujillo. Gradient Augmented Reinitialization Scheme for the Level Set Method. {\it International Journal of Numerical Methods in Fluids}, 73(12):1011-1041, 2013.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Publication 5 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] Suraj S. Deshpande, **Lakshman Anumolu**, Mario F. Trujillo. Evaluating the performance of the two-phase flow solver interFoam. {\it Computational Science \& Discovery}, 5:014016: 1-36, 2012.
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Publication 6 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	\item[] **Lakshman Anumolu**. {\it Local, Higher Order Accurate, Level Set Redistancing Methods}. Masters thesis, Madison WI, 2011.
    \end{itemize}
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{\sc \large P\small {ROJECTS} } \smallskip
	\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.25pt} \vskip -0.15in
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Project 1 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf Framework to Photorealistic Render Computational Fluid Dynamics Results} \\
	Lakshman Anumolu \hfill {\it 2020 - present}
	\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item Scene templates to process CFD results photorealistically
	\end{itemize}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Project 2 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf MeshIO} \\
	with [Pradeep Garigipati](//pradeepgarigipati.com) \hfill {\it 2015 - present}
	\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item Read and write STL file format
	\end{itemize}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Project 3 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf Basic Model Viewer} \\
	Lakshman Anumolu \hfill {\it 2014 - present}
	\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item Visualizes 3D surface mesh
	\end{itemize}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Project 4 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf Weak Formulation of Gradient Augmented Level Set Method to Stephan Type Problems} \\
	Lakshman Anumolu \hfill {\it 2012 - 2012}
	\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item 3D Crystal growth simulated using PhysBAM
	\end{itemize}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Project 5 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf Simulation of Smoke in OpenFOAM Framework} \\
	with [Imaduddin Ahmed](https://multiphaseflow.erc.wisc.edu/people/) \hfill {\it 2012 - 2012}
	\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item Smoke simulation using OpenFOAM
	\end{itemize}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Project 6 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf Screensaver using ModernGL} \\
	Lakshman Anumolu \hfill {\it 2013 - 2013}
	\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item Screensaver in ModernGL
	\end{itemize}
	
	%~~~~~~~~~~~~~~~~~~~~~~~~~~ Project 7 ~~~~~~~~~~~~~~~~~~~~~~~~~~%
	{\bf Desktop, web apps, games built while learning app development} \\
	Lakshman Anumolu \hfill {\it 2013 - 2014}
	\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{0mm} \smallskip
	
	\item Facebook friend sentiment analysis
	\item Facebook speech-to-text enabled chat
	\item Air hockey
	\end{itemize}
	
	
	
	
	
	
	
	
	
	
	
	
	\end{resume}
	\end{document}
	